Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-09 Grassmannian_cells.tex
Notation changes in section 4

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition. In particular, every quiver Grassmannian of a lifted preprojective representation admits a cell decomposition.
\end{theorem}
\begin{proof}

>>>>

\begin{theorem}
  \label{cellscover}
  For $m\geq 1$ and $J\subsetneq\{1,\ldots,n\}$, every quiver Grassmannian $\Gr^{\tilde Q}_\tbfe(\tilde P_{m+1}^J)$ admits a cell decomposition.
\end{theorem}
\begin{corollary}
  Every quiver Grassmannian of a lifted preprojective representation admits a cell decomposition.
\end{corollary}
\begin{proof}
  This is the special case $J=\varnothing$ in Theorem~\ref{cellscover}.
\end{proof}
\begin[Proof of Theorem~\ref{cellscover}]{proof}
